Fixing Vulnerabilities Hinders Maintainability

### 2019-02-03 paper/ICPC19/icpc19.tex
fix code

%
% Add comments in the text
%
\newboolean{showcomments}
\setboolean{showcomments}{false}
%\setboolean{showcomments}{false}

@@

There are security flaws that are more difficult to refactor than others. For
instance, implementing secure authentication is not as easy as fixing a cross-site scripting vulnerability with simple function to sanitize data\footnote{More information about \texttt{htmlentities()} at http://php.net/manual/en/function.htmlentities.php (Accessed on \today{})}. Knowing which patterns are more likely to increase maintainability
issues is one step forward to bring awareness to security engineers of what
patterns need more attention. The taxonomy of security patterns used to answer
this question is the same as the one provided by the authors of the dataset~\cite{Reis:2017:IJSSE}.
Maintainability is measured separately for each pattern.

\setcounter{lstannotation}{0}
\begin{lstlisting}[style={PHPStyle}, caption={Fix provided by \texttt{nextcloud/server} developers to a \\Cross-Site Scripting vulnerability},label={lst:fix},language=php]
 <ul>
    <li class='error'>
       <?php echo $l->t('Cloud not found');?><br/>
-      <p class='hint'><?php if(isset($_['file'])) echo $_['file']?></p>
+      <p class='hint'><?php if(isset($_['file'])) echo htmlentities($_['file'])?></p>
    </li>
 </ul>

>>>>

%
% Add comments in the text
%
\newboolean{showcomments}
\setboolean{showcomments}{true}
%\setboolean{showcomments}{false}

@@

There are security flaws that are more difficult to refactor than others. For
instance, implementing secure authentication is not as easy as fixing a cross-site scripting vulnerability
since usually the last one is fixed within a line or two of code, as seen in Figure~\ref{lst:fix}. 
Knowing which patterns are more likely to increase maintainability
issues is one step forward to bring awareness to security engineers of what
patterns need more attention. The taxonomy of security patterns used to answer
this question is the same as the one provided by the authors of the dataset~\cite{Reis:2017:IJSSE}.
Maintainability is measured separately for each pattern.

\setcounter{lstannotation}{0}
\begin{lstlisting}[style={PHPStyle}, caption={Fix provided by \texttt{nextcloud/server} developers to a \\Cross-Site Scripting vulnerability},label={lst:fix}]
 <ul>
    <li class='error'>
       <?php echo $l->t('Cloud not found');?><br/>
-      <p class='hint'><?php if(isset($_['file'])) echo $_['file']?></p>
+      <p class='hint'><?php if(isset($_['file'])) echo htmlentities($_['file'])?></p>
    </li>
 </ul>
